---
title: "Hybrid recommendation systems based on bayesian network"
author: "Chenxi He, Shengqian Chen, Wenxue Zhang"
date: "March 16, 2016"
output: beamer_presentation
---

##Canonical weighted sum

Let $X_i$ be a node in a BN, let $Pa(X_i)$ be the parent set of $X_i$, and $Y_k$ be the $k^{\mathrm{th}}$ parent of $X_i$ in the BN.  By using a canonical weighted sum, the set of conditional probability distributions stored at node $X_i$ are then represented by means of

$$ Pr(x_{ij}\mid pa(X_i)) = \sum_{Y_k\in Pa(X_i)}w(y_{k,l},x_{i,j})$$

where $w(y_{k,l},x_{i,j})$ are weights(effects) measuring how this $l^{\mathrm{th}}$ value of variable $Y_k$ describes the $j^{\mathrm{th}}$ state of node $X_i$.

$$ \sum_{j=1}^{r} \sum_{Y_k\in Pa(X_i)} w(y_{k,l},x_{i,j}) =1$$

##Related theorems

**Theorem 1**
$Pr(x_{a,s}\mid ev) = \sum_{j=1}^{m_{x_{a}}}\sum_{k=1}^{l_{Y_{j}}}w(y_{j,k},x_{a,s})\cdot Pr(y_{j,k}\mid ev)$

**Theorem 2**  
if $F_k\notin Pa(I_j)$   
$Pr(f_{k,1}\mid i_{j,1}) = Pr(f_{k,1})$  

if $F_k\in Pa(I_j)$  
$Pr(f_{k,1}\mid i_{j,1}) = Pr(f_{k,1}) + \frac{w(f_{k,1},i_{j,1})Pr(f_{k,1}(1-Pr(f_{k,1}))}{Pr(i_{j,1})}$

where $Pr(i_{j,1}) = \sum_{F_k\in Pa(I_j)}w(f_{k,1},i_{j,1})Pr(f_{k,1})$

##Algorithm(Now we've completed CB and we'll further develop CF and hybrid part later)

1.Content-based propagation:  
-$ev_{cb}==I_j\quad Pr(i_{j,1}\mid ev) = 1$  
$\,$ Compute $Pr(F_k\mid ev)$ using Theorem 2  
-Propagate to items using Theorem1.   
-Propagate to $A_{CB}$ and $U_i\in U_1^-$ using Theorem 1.

2.Collaborative propagation

3.Combine content-based and collaborative likelihoods at hybrid node $A_H$  

4.Select the predicted rating.


## example data
- features $\{f_1,f_2,f_3,f_4\}$
- movies $\{i_1,i_2,i_3\}$
- users $\{u_1,u_2\}$

table1: row:movies;  column:features;  entry:{0,1}

$\left(\begin{array}{cccc} 1&0&0&1\\0&1&1&1\\1&1&0&1 \end{array}\right)$

table2: row:user;  column:movies;  entry:{0,1-5}

$\left(\begin{array}{ccc} 0&3&5\\4&2&4 \end{array}\right)$

Here we try to predict what user1 will rate item1.

## CB-part Algorithm Application in the previous data

```{r,echo=FALSE,message=FALSE, warning=FALSE}
data1=matrix(c(1,0,0,1,0,1,1,1,1,1,0,1),byrow=TRUE,nrow=3)
data2=matrix(c(0,3,5,4,2,4),byrow=TRUE,nrow=2)
#nk vector
nk=colSums(data1!= 0)
item.num=dim(data1)[1]
feature.num=dim(data1)[2]
# M.vector normalizing factor vector 
M.vector=data1 %*% (as.matrix(log(item.num/colSums(data1)+1)))
#table3_ij row:item; col: feature; entry:w_item,feature
table3= t(t(data1) * ((log(item.num/nk+1)))) * as.vector((1/M.vector))
#calculate w_iu : 1/|I(U_cb)| vector
w_iu=function(user.rate=1,user=1){
  r=data2[user,]
  t=r
  t[which((t-user.rate)!=0)]=0
  t[which((t-user.rate)==0)]=1/length(which((r)!=0))
  return(t)
}
#function x={user,item} y=c(p(r=1),...,p(r=5))

#let i=1,u=1 important!!!!!!!!!!!!!!!!!!!!!!!!!!!!
i=1
u=1
  #item instantiation e_vb==i
  p.itemgivenev=rep(0,item.num)
  #propagating towards features,using thereom 2,EP
  p.f=1/feature.num
  #p.item
  p.item=sum(table3[i,]*p.f)
  #p(f|ev)
  p.featuregivenev=rep(p.f,feature.num)+table3[i,]*p.f*(1-p.f)/p.item
  
  #propagating to items using thereom 1 p(I|ev), only need to calculate items user u has rated
  p.itemgivenev=table3 %*% as.matrix(p.featuregivenev)
  p.itemgivenev[i,1]=1
  
  #propagating to user rate using thereom 1
  wui_rate0=w_iu(user.rate = 0,user = 1)
  wui_rate1=w_iu(user.rate = 1,user = 1)
  wui_rate2=w_iu(user.rate = 2,user = 1)
  wui_rate3=w_iu(user.rate = 3,user = 1)
  wui_rate4=w_iu(user.rate = 4,user = 1)
  wui_rate5=w_iu(user.rate = 5,user = 1)
  p=c(sum(wui_rate0 * p.itemgivenev),sum(wui_rate1 * p.itemgivenev),sum(wui_rate2 * p.itemgivenev),sum(wui_rate3 * p.itemgivenev),sum(wui_rate4 * p.itemgivenev),sum(wui_rate5 * p.itemgivenev))
```

First we need to calculate the canonical weight in two circumstance (item,feature) and (item,user)
```{r}
table3
wui_rate3
```


Now we can compute the $Pr(F_k\mid ev)$, here in this example $evidence_{cb}$ is $I_1$, so it's a vector $P(F_k\mid I_1)$ 
```{r}
p.featuregivenev
```

Then the information propagate to items using Theorem1 we can get the vector $P(I_k \mid I_1)$ 

##CB-part Algorithm Application in the previous data
```{r}
t(p.itemgivenev)
```

Finally we can get the probabiliy how the user will rate the item:
```{r}
t(p)
```
